A common misapplication of statistical inference: nuisance control with null-hypothesis significance tests

### 2016-07-06 simulation/statfail.Rmd
republish on RPubs

---
title: 'A common misapplication of statistical inference: nuisance control with null-hypothesis significance test'
author: "Phillip M. Alday"
date: "May  2016"
output: 
  html_document:
    toc: TRUE
    toc_float: TRUE
    code_folding: hide
    self_contained: TRUE
    highlight: textmate
params:
  n: 500
  use_plotly: FALSE
  cores: 2
---

>>>>

---
title: 'A common misapplication of statistical inference: nuisance control with null-hypothesis significance tests'
author: "Phillip M. Alday"
date: "July  2016"
output: 
  html_document:
    toc: TRUE
    toc_float: TRUE
    code_folding: hide
    self_contained: TRUE
    highlight: textmate
params:
  n: 500
  use_plotly: FALSE
  cores: 2
---
